---
title: "Download Care Compare Files"
output:
html_notebook: default
---

This script downloads the relevant data to the folder "zips", with a subdirectory for each Care Compare report.

```{r, echo=TRUE, eval=FALSE}
source("init.R")

library(rvest)

yearly_dir <- file.path(dirs$zip, "yearly")

dir.create(dirs$zip, showWarnings = FALSE)
dir.create(yearly_dir, showWarnings = FALSE)
```


Manually construct the URLs for the "yearly" zip files, from this URL:
<https://data.cms.gov/provider-data/archived-data/hospitals>

```{r}
cms_base_url <-
  "https://data.cms.gov/provider-data/sites/default/files/archive/Hospitals/"

make_zip_link <- function(x, archive = TRUE) {
  if (archive) {
    str_c(cms_base_url, x, "/hospitals_archive_", x, ".zip")
  } else {
    str_c(cms_base_url, x, "/hospitals_", x, ".zip")
  }
}

yearly_zip_urls <- c(
  sapply(2015:2020, make_zip_link), sapply(2021:2022, make_zip_link, FALSE)
)
```


Download the yearly zip files

```{r, echo=TRUE, eval=TRUE, include=TRUE}
for (zip in yearly_zip_urls) {
  destfilename <- file.path(yearly_dir, basename(zip))
  if (!file.exists(destfilename)) {
    download.file(url = zip, destfile = destfilename)
  }
}

yearly_files <- list.files(yearly_dir)
yearly_files <-
  file.path(yearly_dir, yearly_files[grepl("[.]zip$", yearly_files)])

yearly_files
```


Unzip the yearly archives and delete the zip files

```{r}
for (zip in yearly_files) {
  unzip(zip, exdir = dirs$zip)
}
unlink(yearly_dir, recursive = TRUE)
```


Delete some of the unneeded Care Compare zip files (the ones starting with "hos_archive" or "va_data_archive")

```{r}
zip_files <- list.files(dirs$zip)
zip_files <- file.path(dirs$zip, zip_files[grepl("[.]zip$", zip_files)])

to_delete <- grepl("/(hos|va_data)_archive", zip_files)
for (zip in zip_files[to_delete]) {
  unlink(zip)
}
zip_files <- zip_files[!to_delete]
```


Unzip the remaining reports and delete the zip files

```{r}
for (zip in zip_files) {
  unzipped_name <- file.path(dirs$zip, str_split(basename(zip), "[.]")[[1]][1])
  unzip(zip, exdir = unzipped_name)
  unlink(zip)
}
```








