---
title: "R Notebook"
output:
html_notebook: default
---

```{r}
source("init.R")
library(data.table)

load(file = file.path(dirs$rdata, "all_data_list.RData"))

all_mort_readm_data_df <- all_data_list$all_mort_readm_data_df
all_maternal_data_df   <- all_data_list$all_maternal_data_df
all_hai_data_df        <- all_data_list$all_hai_data_df
all_hcahps_data_df     <- all_data_list$all_hcahps_data_df
all_timely_data_df     <- all_data_list$all_timely_data_df
all_imaging_data_df    <- all_data_list$all_imaging_data_df
all_ipfqr_data_df      <- all_data_list$all_ipfqr_data_df
all_hospital_info_df   <- all_data_list$all_hospital_info_df
all_measure_info_df    <- all_data_list$all_measure_info_df
all_va_hospital_df     <- all_data_list$all_va_hospital_df
all_sas_input_df       <- all_data_list$all_sas_input_df
all_national_rates_df  <- all_data_list$all_national_rates_df
measure_id_history_df  <- all_data_list$measure_id_history_df
```




```{r}
latest_sas_measures_df <-
  all_measure_info_df %>%
  filter(cc_date == "2023-01-01", !is.na(sas_measure_id)) %>%
  #filter(cc_date == "2021-07-01", !is.na(sas_measure_id)) %>%
  select(measure_id_sas = sas_measure_id, measure_id_std = measure_id,
         measure_group, higher_is_better, sas_measure_id, sas_measure_stat)

sas_measure_id_conversion_df <-
  measure_id_history_df %>%
  filter(cc_date >= "2018-01-01") %>%
  pivot_longer(
    -cc_date, names_to = "measure_id_std", values_to = "measure_id_historical"
  ) %>%
  filter(!is.na(measure_id_historical))

sas_measure_df <-
  latest_sas_measures_df %>%
  left_join(sas_measure_id_conversion_df, by = "measure_id_std") %>%
  mutate(
    measure_id_sas = case_when(
      measure_id_sas == "PSI_4_SURG_COMP" ~ "PSI_04",
      measure_id_sas == "PSI_90_SAFETY"   ~ "PSI_90",
      TRUE ~ measure_id_sas
    )
  ) %>%
  arrange(measure_id_std, cc_date)

sas_measure_df %>%
  filter(grepl("IMM", measure_id_sas) | grepl("IMM", measure_id_std))
```



# Measures besides HAI and HCAHPS

```{r}
sas_most_groups_df <-
  bind_rows(
    all_mort_readm_data_df %>%
      filter(cc_date >= "2018-01-01") %>% select(cc_date, data),
    all_maternal_data_df %>%
      filter(cc_date >= "2018-01-01") %>% select(cc_date, data),
    all_timely_data_df %>%
      filter(cc_date >= "2018-01-01") %>% select(cc_date, data),
    all_imaging_data_df %>%
      filter(cc_date >= "2018-01-01") %>% select(cc_date, data)
  ) %>%
  unnest(data) %>%
  filter(!(
    (measure_id == "IMM_3") & (provider_id == "220126") & (is.na(score))
  )) %>%
  #filter(cc_date <= "2019-01-01", grepl("IMM", measure_id)) %>%
  inner_join(
    sas_measure_df,
    by = c("cc_date", "measure_id" = "measure_id_historical")
  ) %>%
  select(
    cc_date,
    provider_id,
    measure_id_sas,
    score,
    DEN
  ) %>%
  pivot_wider(
    id_cols = c(cc_date, provider_id),
    names_from  = measure_id_sas,
    names_glue  = "{measure_id_sas}_{.value}",
    values_from = c(score, DEN)
  )

colnames(sas_most_groups_df) <-
  gsub("_score$", "", colnames(sas_most_groups_df))

sas_most_groups_df %>% select(cc_date, provider_id, IMM_3)


all_measure_info_df %>%
  filter(cc_date >= "2018-01-01", grepl("PSI.*(0?4|90)", measure_id)) %>%
  filter(!is.na(sas_measure_id))

temp_df <- all_timely_data_df %>% filter(cc_date == "2018-01-01")
temp_df$data[[1]] %>% count(measure_id)
sas_measure_df %>% filter(grepl("IMM", measure_id_historical))
```


# HAI

```{r}
sas_hai_df <-
  all_hai_data_df %>%
  filter(cc_date >= "2018-01-01") %>%
  select(cc_date, data) %>%
  unnest(data) %>%
  filter(!is.na(CI_LOWER) | !is.na(CI_UPPER)) %>%
  select(
    cc_date,
    provider_id,
    measure_id,
    SIR,
    DEN_PRED,
    DEN_VOL
  ) %>%
  pivot_wider(id_cols = c(cc_date, provider_id),
              names_from = measure_id,
              names_glue = "{measure_id}_{.value}",
              values_from = c(SIR, DEN_PRED, DEN_VOL))

colnames(sas_hai_df) <- gsub("_SIR$", "", colnames(sas_hai_df))

sas_hai_df
```



# HCAHPS

```{r}
temp_sas_hcahps_df <-
  all_hcahps_data_df %>%
  filter(cc_date >= '2018-01-01') %>%
  select(cc_date, data) %>%
  unnest(data) %>%
  select(
    cc_date, provider_id, measure_id,
    STAR_RATING, TOP_BOX,
    H_NUMB_COMP, H_RESP_RATE_P
  )

hcahps_star_measure_ids <-
  sas_measure_df %>%
  filter(grepl("H[_].*.[_]STAR_RATING", measure_id_sas)) %>%
  pull(measure_id_std) %>% unique

hcahps_star_df <-
  temp_sas_hcahps_df %>%
  filter(measure_id %in% hcahps_star_measure_ids) %>%
  transmute(cc_date, provider_id, STAR_RATING,
            measure_id = str_c(measure_id, "_STAR_RATING")) %>%
  pivot_wider(id_cols = c(cc_date, provider_id),
              names_from = measure_id, values_from = STAR_RATING)

hcahps_denom_df <-
  temp_sas_hcahps_df %>%
  filter(!(measure_id %in% c("H_INDI","H_GLOB"))) %>%
  select(cc_date, provider_id, H_NUMB_COMP, H_RESP_RATE_P) %>%
  distinct()

sas_hcahps_df <-
  full_join(hcahps_star_df, hcahps_denom_df, by = c("cc_date", "provider_id"))
```


# Combine Columns

```{r}
sas_input_file_hospital_ids <-
  all_hospital_info_df %>%
  filter(cc_date == "2023-01-01", in_sas_input_file) %>%
  pull(provider_id)

sas_df <-
  sas_most_groups_df %>%
  full_join(sas_hai_df, by = c("cc_date", "provider_id")) %>%
  full_join(sas_hcahps_df, by = c("cc_date", "provider_id")) %>%
  rename(PROVIDER_ID = provider_id) %>%
  filter(PROVIDER_ID %in% sas_input_file_hospital_ids)

my_sas_input_df <-
  sas_df %>%
  group_by(cc_date) %>%
  nest()

my_sas_input_df
my_sas_input_df$data[[25]]
```


```{r}
save(my_sas_input_df, file = "rdata/my_sas_input_df.RData")
```




```{r}
library(data.table)
#load("rdata/my_sas_input_df.RData")
load("rdata/measures_202104_dt.rda")
load("rdata/measure_groups_202104_dt.rda")

measures_202104_dt <-
  measures_202104_dt %>%
  mutate(
    measure_std = case_when(
      measure_id == "PSI_4_SURG_COMP" ~ "std_PSI_04",
      measure_id == "PSI_90_SAFETY"   ~ "std_PSI_90",
      TRUE ~ measure_std
    ),
    measure_id = case_when(
      measure_id == "PSI_4_SURG_COMP" ~ "PSI_04",
      measure_id == "PSI_90_SAFETY"   ~ "PSI_90",
      TRUE ~ measure_id
    )
  ) %>%
  as.data.table()

measures_202307_dt <-
  data.table::rbindlist(list(
    measures_202104_dt[
      !(measures_202104_dt$retired_2022), !c("retired_2021", "retired_2022")
    ],
    all_measure_info_df %>%
      filter(measure_id == "HCP_COVID_19", cc_date == "2023-07-01") %>%
      transmute(
        measure_id,
        group_name   = measure_group,
        measure_desc = measure_name,
        flip_sign    = ifelse(higher_is_better == TRUE, 1, -1),
        measure_std  = measure_id
      )
  ))

measure_ref <-
  list(
    "group_dt" = measure_groups_202104_dt,
    "measure_dt" = list(
      "v202104" = measures_202104_dt[, !c("retired_2021", "retired_2022")],
      "v202207" = measures_202104_dt[!measures_202104_dt$retired_2021, !c("retired_2021", "retired_2022")],
      "v202307" = measures_202307_dt
    )
  )

save(measure_ref, file = "rdata/measure_ref.rda")
```


```{r}
# check_column_names <- function(sas_input_dt, measures_dt) {
# 
#   measures_all <- measures_dt$measure_id
#   # if (!all(measures_all  %in% colnames(sas_input_dt))) {
#   #   measures_all <- measures_dt[retired_2021 == FALSE, ]$measure_id
#   #   if (!all(measures_all %in% colnames(sas_input_dt))) {
#   #     measures_all <- measures_dt[retired_2022 == FALSE, ]$measure_id
#   #     if (!all(measures_all %in% colnames(sas_input_dt))) {
#   #       missing <- setdiff(measures_all, colnames(sas_input_dt))
#   #       missing_str <- paste(missing, collapse = ", ")
#   #       stop(paste("sas_input_dt missing columns: ", missing_str))
#   #     }
#   #   }
#   # }
#   measures_all[measures_all %in% colnames(sas_input_dt)]
# }
# 
# sas_step1_standardize_202104 <- function(sas_input_dt) {
# 
#   if (!data.table::is.data.table(sas_input_dt)) {
#     data.table::setDT(sas_input_dt)
#   }
# 
#   measures_all <- check_column_names(sas_input_dt,
#                                      cmsstars::measures_202104_dt)
#   measure_volume <-
#     colSums(
#       sas_input_dt[
#         , ..measures_all
#       ][
#         , (measures_all) := lapply(.SD, function(x) as.integer(!is.na(x))),
#         .SDcols = measures_all
#       ][]
#     )
# 
#   measures_in  <- names(measure_volume[measure_volume >  100])
#   measures_out <- names(measure_volume[measure_volume <= 100])
#   sign_flips <- setNames(measures_202104_dt$flip_sign,
#                          measures_202104_dt$measure_id)
# 
#   scale_and_flip <- function(cname) {
#     scale(sas_input_dt[[cname]]) * sign_flips[cname]
#   }
# 
#   list(
#     'measure_ids' = measures_in,
#     'dt' =
#       sas_input_dt[
#         , !..measures_out
#       ][
#         , (measures_in) := lapply(names(.SD), scale_and_flip)
#         , .SDcols = measures_in
#       ][],
#     'dropped_measure_ids' = measures_out
#   )
# }
# 
# 
# sas_step2_groups_202104 <- function(std_data_dt, measure_ids) {
# 
#   temp_measures_dt <-
#     data.table::merge.data.table(
#       measures_202104_dt[, c("measure_id", "group_name")],
#       measure_groups_202104_dt, by = "group_name"
#     )
# 
#   keep_cols <- c("PROVIDER_ID", measure_ids)
#   group_score_not_std_dt <-
#     data.table::melt.data.table(
#       std_data_dt[, ..keep_cols], "PROVIDER_ID",
#       variable.name = "measure_id", value.name = "value", na.rm = TRUE
#     )[
#       temp_measures_dt, on = "measure_id", nomatch = 0
#     ][
#       , .(
#         score_before_std = mean(value),
#         N = .N,
#         include_group = as.integer(.N >= 3),
#         include_mortsafe = as.integer((sum(mortsafe_flag == 1)) >= 3)
#       )
#       , by = c("PROVIDER_ID", "group_name", "weight")
#     ]
# 
#   group_stats_dt <-
#     group_score_not_std_dt[
#       , .(score_avg = mean(score_before_std),
#           score_sd = sd(score_before_std)), by = "group_name"
#     ]
# 
#   group_scores_dt <-
#     data.table::merge.data.table(
#       group_score_not_std_dt, group_stats_dt, by = c("group_name")
#     )
#   group_scores_dt[
#     , group_score := (score_before_std - score_avg) / score_sd
#   ][]
# }
# 
# 
# compute_star_clusters <- function(summary_score) {
# 
#   quantiles <- stats::quantile(summary_score, probs = 0.2*(1:4), type=1)
# 
#   initial_centers_dt <-
#     data.table::data.table(summary_score = summary_score)[
#       , grp := as.integer(cut(summary_score, breaks = c(-Inf, quantiles, Inf)))
#     ][
#       order(grp),
#       .(summary_score_median = median(summary_score)),
#       by = "grp"
#     ]
# 
#   second_centers <-
#     cmsstars::sas_proc_fastclus(
#       summary_score, initial_centers_dt$summary_score_median, iter.max = 1000
#     )$centers
# 
#   km <- cmsstars::sas_proc_fastclus(
#     summary_score, second_centers, iter.max = 1000, strict = 1
#   )
#   abs(km$cluster)
# }
# 
# sas_step3_stars_202104 <- function(group_scores_dt) {
# 
#   group_scores_pivoted_dt <-
#     data.table::dcast(
#       group_scores_dt, PROVIDER_ID ~ group_name,
#       value.var = c("group_score", "N")
#     )
# 
#   temp_summary_scores_dt <-
#     group_scores_dt[
#       order(PROVIDER_ID), .(
#         n_groups = sum(include_group),
#         n_mortsafe = sum(include_mortsafe),
#         report_indicator = as.integer(sum(include_group) >= 3) *
#           as.integer(sum(include_mortsafe) >= 1),
#         summary_score = sum(weight * group_score) / sum(weight)
#       ), by = "PROVIDER_ID"
#     ]
# 
#   temp_summary_scores_dt[
#     report_indicator == 1,
#     stars := compute_star_clusters(summary_score),
#     by = "n_groups"
#   ]
# 
#   data.table::merge.data.table(
#     group_scores_pivoted_dt, temp_summary_scores_dt,
#     by = "PROVIDER_ID", all.x = TRUE
#   )
# }
# 
# compute_star_scores_202104 <- function(sas_input_dt) {
# 
#   init_list <- sas_step1_standardize_202104(sas_input_dt)
#   group_scores_dt <- sas_step2_groups_202104(init_list$dt,
#                                              init_list$measure_ids)
#   final_dt <- sas_step3_stars_202104(group_scores_dt)
#   data.table::merge.data.table(sas_input_dt, final_dt, by = "PROVIDER_ID",
#                                all.x = TRUE)
# }
```


```{r}
check_column_names <- function(sas_input_dt, measures_dt) {

  measures_all <- measures_dt$measure_id
  # if (!all(measures_all  %in% colnames(sas_input_dt))) {
  #   measures_all <- measures_dt[retired_2021 == FALSE, ]$measure_id
  #   if (!all(measures_all %in% colnames(sas_input_dt))) {
  #     measures_all <- measures_dt[retired_2022 == FALSE, ]$measure_id
  #     if (!all(measures_all %in% colnames(sas_input_dt))) {
  #       missing <- setdiff(measures_all, colnames(sas_input_dt))
  #       missing_str <- paste(missing, collapse = ", ")
  #       stop(paste("sas_input_dt missing columns: ", missing_str))
  #     }
  #   }
  # }
  measures_all[measures_all %in% colnames(sas_input_dt)]
}


sas_step1_standardize_202307 <- function(sas_input_dt) {

  if (!data.table::is.data.table(sas_input_dt)) {
    data.table::setDT(sas_input_dt)
  }

  measures_all <- check_column_names(sas_input_dt, measures_202307_dt)
  measure_volume <-
    colSums(
      sas_input_dt[
        , ..measures_all
      ][
        , (measures_all) := lapply(.SD, function(x) as.integer(!is.na(x))),
        .SDcols = measures_all
      ][]
    )

  measures_in  <- names(measure_volume[measure_volume >  100])
  measures_out <- names(measure_volume[measure_volume <= 100])
  sign_flips <- setNames(measures_202307_dt$flip_sign,
                         measures_202307_dt$measure_id)

  scale_and_flip <- function(cname) {
    scale(sas_input_dt[[cname]]) * sign_flips[cname]
  }

  list(
    'measure_ids' = measures_in,
    'dt' =
      sas_input_dt[
        , !..measures_out
      ][
        , (measures_in) := lapply(names(.SD), scale_and_flip)
        , .SDcols = measures_in
      ][],
    'dropped_measure_ids' = measures_out
  )
}


sas_step2_groups_202307 <- function(std_data_dt, measure_ids) {

  temp_measures_dt <-
    data.table::merge.data.table(
      measures_202307_dt[, c("measure_id", "group_name")],
      measure_groups_202104_dt, by = "group_name"
    )

  keep_cols <- c("PROVIDER_ID", measure_ids)
  group_score_not_std_dt <-
    data.table::melt.data.table(
      std_data_dt[, ..keep_cols], "PROVIDER_ID",
      variable.name = "measure_id", value.name = "value", na.rm = TRUE
    )[
      temp_measures_dt, on = "measure_id", nomatch = 0
    ][
      , .(
        score_before_std = mean(value),
        N = .N,
        include_group = as.integer(.N >= 3),
        include_mortsafe = as.integer((sum(mortsafe_flag == 1)) >= 3)
      )
      , by = c("PROVIDER_ID", "group_name", "weight")
    ]

  group_stats_dt <-
    group_score_not_std_dt[
      , .(score_avg = mean(score_before_std),
          score_sd = sd(score_before_std)), by = "group_name"
    ]

  group_scores_dt <-
    data.table::merge.data.table(
      group_score_not_std_dt, group_stats_dt, by = c("group_name")
    )
  group_scores_dt[
    , group_score := (score_before_std - score_avg) / score_sd
  ][]
}


compute_star_clusters <- function(summary_score) {

  quantiles <- stats::quantile(summary_score, probs = 0.2*(1:4), type=1)

  initial_centers_dt <-
    data.table::data.table(summary_score = summary_score)[
      , grp := as.integer(cut(summary_score, breaks = c(-Inf, quantiles, Inf)))
    ][
      order(grp),
      .(summary_score_median = median(summary_score)),
      by = "grp"
    ]

  second_centers <-
    hospitalstars::sas_proc_fastclus(
      summary_score, initial_centers_dt$summary_score_median, iter.max = 1000
    )$centers

  km <- hospitalstars::sas_proc_fastclus(
    summary_score, second_centers, iter.max = 1000, strict = 1
  )
  abs(km$cluster)
}


sas_step3_stars_202104 <- function(group_scores_dt) {

  group_scores_pivoted_dt <-
    data.table::dcast(
      group_scores_dt, PROVIDER_ID ~ group_name,
      value.var = c("group_score", "N")
    )

  temp_summary_scores_dt <-
    group_scores_dt[
      order(PROVIDER_ID), .(
        n_groups = sum(include_group),
        n_mortsafe = sum(include_mortsafe),
        report_indicator = as.integer(sum(include_group) >= 3) *
          as.integer(sum(include_mortsafe) >= 1),
        summary_score = sum(weight * group_score) / sum(weight)
      ), by = "PROVIDER_ID"
    ]

  temp_summary_scores_dt[
    report_indicator == 1,
    stars := compute_star_clusters(summary_score),
    by = "n_groups"
  ]

  data.table::merge.data.table(
    group_scores_pivoted_dt, temp_summary_scores_dt,
    by = "PROVIDER_ID", all.x = TRUE
  )
}

compute_star_scores_202307 <- function(sas_input_dt) {

  init_list <- sas_step1_standardize_202307(sas_input_dt)
  group_scores_dt <- sas_step2_groups_202307(init_list$dt,
                                             init_list$measure_ids)
  final_dt <- sas_step3_stars_202104(group_scores_dt)
  data.table::merge.data.table(sas_input_dt, final_dt, by = "PROVIDER_ID",
                               all.x = TRUE)
}
```




```{r}
# sas_package_data_df <-
#   my_sas_input_df %>%
#   mutate(sas_output_df = map(data, compute_star_scores_202104)) %>%
#   select(-data)
```


```{r}
load(file = "rdata/my_sas_input_df.RData")
```


```{r}
# library(hospitalstars)
# sas_package_data_df <-
#   my_sas_input_df %>%
#   mutate(sas_output_df = map(data, hospitalstars::compute_star_scores)) %>%
#   select(-data)
```



## Note about the 2023-01 SAS input

When scores are reported in both the 2023-01 Care Compare report and in the SAS input file released July '23, the scores are the same. However, there are about 7 Process measures (IMM_3,OP_22,OP_13,OP_29,SEP_1,OP18B,OP_10) where a significant number of hospitals have a score that's either (a) reported only in the Care Compare data or (b) reported only in the SAS sample input file.

There wasn't a clear pattern explaining why scores may be reported in one source but not the other. For all 7 measures, the problem above occurred in no more than 6% of the hospitals that had a score reported in at least one of the sources. So there didn't seem to be other discrepancies between these two data sources.

To avoid confusion in reporting, I replaced the SAS input constructed from Care Compare reports with the SAS sample input. Then all computations were consistent with CMS's preview reports.

```{r}
library(hospitalstars)

to_replace   <- which(my_sas_input_df$cc_date == "2023-01-01")
replace_with <- which(all_sas_input_df$cc_date == "2023-01-01")

my_sas_input2_df <- my_sas_input_df
sas_replacement_df <- all_sas_input_df$data[[replace_with]] %>%
  rename(
    PSI_04 = PSI_4_SURG_COMP, PSI_90 = PSI_90_SAFETY,
    PSI_04_DEN = PSI_4_SURG_COMP_DEN, PSI_90_DEN = PSI_90_SAFETY_DEN
  ) %>%
  select_at(colnames(my_sas_input2_df$data[[to_replace]]))
my_sas_input2_df$data[[to_replace]] <- sas_replacement_df

sas_package_data_df <-
  my_sas_input2_df %>%
  mutate(sas_output_df = map(data, hospitalstars::compute_star_scores)) %>%
  select(-data)
```






```{r}
save(sas_package_data_df, file = "rdata/sas_package_data_df.RData")
```







```{r}
my_sas_input_df$data[[24]]
colnames(my_sas_input_df$data[[24]])

hospitalstars::compute_star_scores(my_sas_input_df$data[[24]])
hospitalstars::sas_package$v202307$input_df
hospitalstars::sas_package$v202307
hospitalstars::compute_star_scores(hospitalstars::sas_package$v202307$input_df)

sas_package_data_df %>%
  transmute(
    cc_date,
    x = map_int(sas_output_df, nrow)
  )
```




```{r}
geis_df <-
  hospital_info_df %>%
  filter(grepl("GEISINGER", hospital_name)) %>%
  select(PROVIDER_ID, hospital_name)

geis_df <-
  geis_df %>%
  inner_join(sas_package_data_df$sas_output_df[[16]][, -(2:95)])

colnames(geis_df)[1:7] <- c("provider_id", "hospital", "mortality", "pt_exp", "process", "readmission", "safety")
geis_df <- geis_df[, c(1:7, 16)]
geis_df
```



```{r}
sas_package_data_df$cc_date[[16]]
sas_package_data_df$sas_output_df[[16]] %>%
  select(PROVIDER_ID, OP_10)
```




```{r}
sas_package_data_df$sas_output_df[[22]]
colnames(sas_package_data_df$sas_output_df[[22]])
```





```{r}
sas_dt <- as.data.table(my_sas_input_df$data[[12]])
sas_col_order <- colnames(all_sas_input_df$data[[15]])
sas_col_order <- sas_col_order[sas_col_order %in% colnames(sas_dt)]
sas_dt <- sas_dt[, ..sas_col_order]
cms_dt <- all_sas_input_df$data[[15]]

sas_dt
cms_dt

compare_col_vals <- function(col_name) {
  inner_join(
      sas_dt %>% select_at(c("PROVIDER_ID", col_name)) %>%
        rename_at(all_of(col_name), function(x) str_c("me")),
      cms_dt %>% select_at(c("PROVIDER_ID", col_name)) %>%
        rename_at(all_of(col_name), function(x) str_c("cms")),
      by = "PROVIDER_ID"
    ) %>%
    mutate(same = (me == cms)) %>%
    count(same)
}

tibble(col_name = colnames(sas_dt)[-1]) %>%
  mutate(compare_df = map(col_name, compare_col_vals)) %>%
  unnest(compare_df) %>%
  filter(!same | is.na(same))


my_stars <- compute_star_scores_202104(sas_dt)

cms_stars <-
  all_hospital_info_df %>%
  filter(cc_date == "2021-04-01") %>%
  select(PROVIDER_ID = provider_id, overall_rating)

compare_stars_df <-
  my_stars %>%
  select(PROVIDER_ID, stars) %>%
  inner_join(cms_stars, by = "PROVIDER_ID") %>%
  mutate(same = (stars == overall_rating))

table(compare_stars_df$same) / nrow(compare_stars_df %>% filter(!is.na(same)))
table(compare_stars_df$stars, compare_stars_df$overall_rating)
```



```{r}
find_blank_measures <- function(df) {
  df %>%
    pivot_longer(-PROVIDER_ID, names_to = "measure_id", values_to = "score") %>%
    group_by(measure_id) %>%
    summarize(n = n(), na_count = sum(is.na(score)), .groups = "drop") %>%
    filter(n == na_count) %>%
    pull(measure_id)
}

missing_measure_df <-
  my_sas_input_df %>%
  mutate(measure_id = map(data, find_blank_measures)) %>%
  select(-data) %>%
  unnest(measure_id) %>%
  mutate(den = grepl("_DEN$", measure_id)) %>%
  filter(!den) %>%
  select(-den) %>%
  mutate(x = "x") %>%
  pivot_wider(names_from = measure_id, values_from = x, values_fill = "")

missing_measure_df
```


```{r}
new_2018_07       <- c("EDAC_30_PN", "SEP_1") # Readmission, Process
new_in_2020       <- c("OP_36", "OP_35_ADM", "OP_35_ED") # Readmission
delayed_1_quarter <- c("OP_32", "OP_35_ADM", "OP_35_ED") # Readmission
delayed_2_quarters <- c("MORT_30_PN", "PSI_4_SURG_COMP", "PSI_90_SAFETY") # Mortality, Mortality, Safety
moved_to_new_file <- c("PC_01") # Process
retired_in_2022   <- c("OP_33") # Process

all_measure_info_df %>% filter(cc_date == "2021-07-01") %>%
  filter(!is.na(sas_measure_id)) %>%
  select(measure_group, measure_id) %>%
  arrange(measure_group, measure_id)

all_measure_info_df %>% filter(measure_id == "EDAC_30_PN")
all_measure_info_df %>% filter(measure_id %in% new_in_2020)
all_measure_info_df %>% filter(grepl("EDAC", measure_id)) %>% count(care_compare_filename)
all_measure_info_df %>% filter(grepl("EDAC", measure_id), grepl("Returns", care_compare_filename))
all_mort_readm_data_df$data[[30]]
all_mort_readm_data_df %>%
  select(-data) %>%
  filter(grepl("Unplanned", filename))
all_measure_info_df %>% filter(measure_id == "OP_10") %>% arrange(desc(cc_date))
```




```{r}
sas_package_data_df$sas_output_df[[20]][, -(2:95)]
sas_package_data_df$sas_output_df[[20]] %>% pull(n_groups) %>% table
sas_package_data_df$sas_output_df[[15]] %>% pull(n_groups) %>% table
sas_package_data_df$sas_output_df[[16]] %>% pull(n_groups) %>% table

sas_package_data_df$sas_output_df[[20]] %>% pull(stars) %>% table
sas_package_data_df$sas_output_df[[15]] %>% pull(stars) %>% table
sas_package_data_df$sas_output_df[[16]] %>% pull(stars) %>% table

na_counts <-
  lapply(sas_package_data_df$sas_output_df[[20]],
         function(x) sum(is.na(x)) / length(x)) %>% unlist
na_counts[order(na_counts, decreasing = TRUE)]
na_counts <- na_counts[order(names(na_counts))]
missing_cols <- names(na_counts[na_counts == 1])
missing_cols[!grepl("_DEN$", missing_cols)]
```

