---
title: "R Notebook"
output:
html_notebook: default
---


```{r}
library(data.table)
library(tidyverse)
library(haven)
```



```{r}
kmeans_Lloyd <- function(x, centers, maxiter, strict) {
  
  n <- length(x)
  k <- length(centers)
  cl <- integer(n)
  
  for (iter in 1:maxiter) {
    x_dt <- data.table(xid = 1:length(x), x = x, cid = cl)
    c_dt <- data.table(cid = 1:length(centers), center = centers)
    
    temp_dt <-
      merge(
        x_dt[, `:=`(old_cid = cid, dummy = 1)][, -"cid"][],
        c_dt[, dummy := 1][],
        by = "dummy", allow.cartesian = TRUE
      )[
        , `:=`(dist = abs(x-center))
      ][
        order(xid, dist, cid)
      ][
        , .SD[1, c("x", "dist", "cid", "old_cid")], by = "xid"
      ][
        , `:=`(cid = ifelse(dist <= strict, cid, -cid))
      ][
        , `:=`(same = (old_cid == cid))
      ][]
    
    cl <- integer(n)
    cl[temp_dt$xid] <- temp_dt$cid
    
    count_dt <- temp_dt[cid > 0, .(N = .N, center = mean(x)), by = "cid"][]
    
    nc <- integer(k)
    nc[count_dt$cid] <- count_dt$N
    centers <- rep(NA_real_, k)
    centers[count_dt$cid] <- count_dt$center
    
    if (all(temp_dt$same)) {
      break
    }
  }
  
  c_dt <- data.table(center=centers, cid = 1:length(centers))
  wss_dt <-
    merge(x_dt, c_dt, by = "cid")[
      cid > 0, .(wss = sum((x-center)^2)), by = "cid"
    ][]
  
  wss <- numeric(k)
  wss[wss_dt$cid] <- wss_dt$wss
  
  list(
    "cluster" = cl, "centers" = centers, "iter" = iter, "wss" = wss, "nc" = nc
  )
}


sas_proc_fastclus <- function(x, centers, iter.max = 10, strict = Inf) {
  
  m <- length(x)
  if (missing(centers))
    stop("'centers' must be a number or a matrix")
  
  if (length(centers) == 1) {
    stop("centers must have length > 1")
  } else {
    if (any(duplicated(centers))) stop("initial centers are not distinct")
    cn <- NULL
    k <- length(centers)
    
    if (m < k) stop("more cluster centers than data points")
  }
  
  if(iter.max < 1) stop("'iter.max' must be positive")

  Z <- kmeans_Lloyd(x, centers, iter.max, strict)
  
  if (Z$iter > iter.max)
    warning("did not converge in ", iter.max, " iterations", call.=FALSE)
  if (any(Z$nc == 0))
    warning("empty cluster: try a better set of initial centers", call.=FALSE)
  
  cluster <- Z$cluster
  if(!is.null(rn <- rownames(x)))
    names(cluster) <- rn
  
  out <- list(cluster = cluster, centers = Z$centers, withinss = Z$wss,
              size = Z$nc)
  class(out) <- "kmeans"
  out
}
```






# 0 - Data and Measure Standardization_2021Apr_E

```{r}
include_retired <- TRUE
retired_measures <- c("OP_30","ED_2B")

all_data_filename <- "all_data_2021apr.sas7bdat"
all_data_df <- haven::read_sas(all_data_filename)
# all_data_df <-
#   all_sas_df %>%
#   filter(zip_date == "2021-04-01") %>%
#   select(sas_input_df) %>%
#   unnest(sas_input_df)

measures_outcomes_mortality <- c(
  'MORT_30_AMI', 'MORT_30_CABG', 'MORT_30_COPD', 'MORT_30_HF',
  'MORT_30_PN', 'MORT_30_STK', 'PSI_4_SURG_COMP'
)
measures_outcomes_safety <- c(
  'COMP_HIP_KNEE',  'HAI_1', 'HAI_2', 'HAI_3',
  'HAI_4', 'HAI_5', 'HAI_6', 'PSI_90_SAFETY'
)
measures_outcomes_readmission <- c(
  'EDAC_30_AMI', 'EDAC_30_HF', 'EDAC_30_PN', 'OP_32',
  'READM_30_CABG', 'READM_30_COPD', 'READM_30_HIP_KNEE', 
  'READM_30_HOSP_WIDE', 'OP_35_ADM', 'OP_35_ED', 'OP_36'
)
measures_pt_exp <- c(
  'H_COMP_1_STAR_RATING', 'H_COMP_2_STAR_RATING', 'H_COMP_3_STAR_RATING',
  'H_COMP_5_STAR_RATING', 'H_COMP_6_STAR_RATING', 'H_COMP_7_STAR_RATING',
  'H_GLOB_STAR_RATING', 'H_INDI_STAR_RATING'
)
measures_process <- c(
  'IMM_3', 'OP_22', 'OP_23',  'OP_29', 'OP_30','OP_33', 'PC_01', 'SEP_1',
  'ED_2B', 'OP_2', 'OP_3B', 'OP_18B', 'OP_8', 'OP_10', 'OP_13'
)
if (!include_retired) {
  measures_process <- setdiff(measures_process, retired_measures)
}
measure_all <- c(
  measures_outcomes_mortality, measures_outcomes_safety,
  measures_outcomes_readmission, measures_pt_exp, measures_process
)
```


```{r}
measure_volume0 <-
  all_data_df[, measure_all] %>%
  summarize(
    across(everything(), function(x) { sum(!is.na(x)) })
  )
measure_volume_t0 <- t(measure_volume0)

include_measure0 <- tibble(
  freq            = measure_volume_t0[, 1],
  measure_in_name = rownames(measure_volume_t0),
  measure_in_std  = str_c("std_", rownames(measure_volume_t0))
)
measure_in_name <- include_measure0$measure_in_name
# %put &measure_in;
measure_cnt <- nrow(measure_in_name)
measure_volume <- measure_volume0
measure_volume_t <- measure_volume_t0
less100_measure <- tibble(
  freq = measure_volume_t[measure_volume_t <= 100],
  measure_name = rownames(measure_volume_t)[measure_volume_t <= 100]
)
# DATA R.less100_measure;SET less100_measure;run;*OP-2;
less100_measure_df <- less100_measure
measure_exclude <- less100_measure$measure_name
initial_data_df <-
  all_data_df[, setdiff(colnames(all_data_df), measure_exclude)]
include_measure <- 
  tibble(
    freq            = measure_volume_t[, 1],
    measure_in_name = rownames(measure_volume_t),
    measure_in_std  = str_c("std_", rownames(measure_volume_t))
  ) %>%
  filter(freq > 100)
measure_in <- include_measure$measure_in_name
measure_in_std <- include_measure$measure_in_std
measure_cnt <- nrow(include_measure)


std_data_analysis_df %>% filter(PROVIDER_ID == "400127")
all_data_df %>% filter(PROVIDER_ID == "400127")
std_data_df %>% filter(PROVIDER_ID == "400127")
initial_data_df %>% filter(PROVIDER_ID == "400127")
```



```{r}
outcomes_mortality <-
  tibble(
    col1 = measure_volume_t[, 1],
    measure_in_name = rownames(measure_volume_t)
  ) %>%
  mutate(measure_in_std = str_c("std_", measure_in_name)) %>%
  filter(col1 > 100, measure_in_name %in% measures_outcomes_mortality)
measure_om <- outcomes_mortality$measure_in_std

outcomes_safety <-
  tibble(
    col1 = measure_volume_t[, 1],
    measure_in_name = rownames(measure_volume_t)
  ) %>%
  mutate(measure_in_std = str_c("std_", measure_in_name)) %>%
  filter(col1 > 100, measure_in_name %in% measures_outcomes_safety)
measure_os <- outcomes_safety$measure_in_std

outcomes_readmission <-
  tibble(
    col1 = measure_volume_t[, 1],
    measure_in_name = rownames(measure_volume_t)
  ) %>%
  mutate(measure_in_std = str_c("std_", measure_in_name)) %>%
  filter(col1 > 100, measure_in_name %in% measures_outcomes_readmission)
measure_or <- outcomes_readmission$measure_in_std

ptexp <-
  tibble(
    col1 = measure_volume_t[, 1],
    measure_in_name = rownames(measure_volume_t)
  ) %>%
  mutate(measure_in_std = str_c("std_", measure_in_name)) %>%
  filter(col1 > 100, measure_in_name %in% measures_pt_exp)
measure_ptexp <- ptexp$measure_in_std

process <-
  tibble(
    col1 = measure_volume_t[, 1],
    measure_in_name = rownames(measure_volume_t)
  ) %>%
  mutate(measure_in_std = str_c("std_", measure_in_name)) %>%
  filter(col1 > 100, measure_in_name %in% measures_process)
measure_process <- process$measure_in_std
```


```{r}
keep_hos <- function(initial_data_df, measure_in, measure_cnt) {
  initial_data_df$Total_m_cnt <- rowSums(!is.na(initial_data_df[, measure_in]))
  keep_rows <- rowSums(!is.na(initial_data_df[, measure_in])) > 0
  initial_data_df[keep_rows, ]
}

initial_data_df <- keep_hos(initial_data_df, measure_in, measure_cnt)

summary_funcs <- list(N=length, MIN=min, MAX=max, MEAN=mean, STD=sd)
measure_average_stddev_df <-
  do.call(
    rbind,
    lapply(
      names(summary_funcs),
      function(func_name) {
        initial_data_df[, measure_in] %>%
          summarize(
            across(
              everything(),
              function(x) summary_funcs[[func_name]](x[!is.na(x)])
            )
          ) %>%
          mutate(STAT=func_name) %>%
          relocate(STAT, .before = measure_in[1])
      }
    )
  )

std_data_analysis_df %>% filter(PROVIDER_ID == "400127")
all_data_df %>% filter(PROVIDER_ID == "400127")
std_data_df %>% filter(PROVIDER_ID == "400127")
initial_data_df %>% filter(PROVIDER_ID == "400127")

std_data_df <-
  initial_data_df %>%
  mutate(
    across(all_of(measure_in), scale)
  )

measures_to_flip <- c(
  'MORT_30_AMI', 'MORT_30_CABG', 'MORT_30_COPD', 'MORT_30_HF', 'MORT_30_PN',
  'MORT_30_STK', 'PSI_4_SURG_COMP', 'COMP_HIP_KNEE', 'HAI_1', 'HAI_2', 'HAI_3',
  'HAI_4', 'HAI_5', 'HAI_6', 'PSI_90_SAFETY', 'EDAC_30_AMI', 'EDAC_30_HF',
  'EDAC_30_PN', 'OP_32', 'READM_30_CABG', 'READM_30_COPD', 'READM_30_HIP_KNEE',
  'READM_30_HOSP_WIDE', 'OP_35_ADM', 'OP_35_ED', 'OP_36', 'OP_22', 'PC_01',
  'OP_3B', 'OP_18B', 'ED_2B', 'OP_8', 'OP_10', 'OP_13'
)
if (!include_retired) {
  measures_to_flip <- setdiff(measures_to_flip, retired_measures)
}
std_data_df[, measures_to_flip] <- -std_data_df[, measures_to_flip]

colnames(std_data_df)[match(measure_in, colnames(std_data_df))] <-
  measure_in_std

std_data_analysis_df <-
  cbind(
    std_data_df[, setdiff(colnames(std_data_df), measure_in_std)],
    std_data_df[, measure_in_std]
  )
```


```{r}
less100_measure_df
measure_average_stddev_df
std_data_analysis_df
```



# 1 - First stage_Simple Average of Measure Scores_2021Apr_E


```{r}
grp_score <- function(indsn, varlist) {
  flag_df <-
    indsn %>%
    select_at(varlist) %>%
    mutate(across(everything(), function(x) as.integer(!is.na(x))))
  colnames(flag_df) <- str_c("C", 1:ncol(flag_df))
  flag_df$total_cnt <- rowSums(!is.na(indsn[, varlist]))
  flag_df$measure_wt <-
    ifelse(flag_df$total_cnt != 0, flag_df$total_cnt, NA_real_)
  flag_df$score_before_std <-
    rowSums(indsn[, varlist], na.rm = TRUE) / flag_df$measure_wt
  flag_df$Mean <- mean(flag_df$score_before_std, na.rm = TRUE)
  flag_df$StdDev <- sd(flag_df$score_before_std, na.rm = TRUE)
  flag_df$grp_score <-
    (flag_df$score_before_std - flag_df$Mean) / flag_df$StdDev
  cbind(indsn[, c('PROVIDER_ID', varlist)], flag_df)
}

std_data_analysis_df %>% filter(PROVIDER_ID == "400127")
all_data_df %>% filter(PROVIDER_ID == "400127")

measure_om_cnt      <- nrow(outcomes_mortality)
measure_os_cnt      <- nrow(outcomes_safety)
measure_or_cnt      <- nrow(outcomes_readmission)
measure_ptexp_cnt   <- nrow(ptexp)
measure_process_cnt <- nrow(process)

outcome_mortality_df   <- grp_score(std_data_analysis_df, measure_om)
outcome_safety_df      <- grp_score(std_data_analysis_df, measure_os)
outcome_readmission_df <- grp_score(std_data_analysis_df, measure_or)
ptexpt_df              <- grp_score(std_data_analysis_df, measure_ptexp)
process_df             <- grp_score(std_data_analysis_df, measure_process)
```



# 2 - Second Stage_Weighted Average and Categorize Star_2021Apr_E_peer


```{r}
all_df <-
  ptexpt_df %>%
  select(PROVIDER_ID, Std_PatientExp_score = grp_score) %>%
  inner_join(
    outcome_safety_df %>%
      select(PROVIDER_ID, Std_Outcomes_Safety_score = grp_score),
    by = 'PROVIDER_ID'
  ) %>%
  inner_join(
    outcome_mortality_df %>%
      select(PROVIDER_ID, Std_Outcomes_Mortality_score = grp_score),
    by = 'PROVIDER_ID'
  ) %>%
  inner_join(
    outcome_readmission_df %>%
      select(PROVIDER_ID, Std_Outcomes_Readmission_score = grp_score),
    by = 'PROVIDER_ID'
  ) %>%
  inner_join(
    process_df %>%
      select(PROVIDER_ID, Std_Process_score = grp_score),
    by = 'PROVIDER_ID'
  )

summary_score <-
  all_df %>%
  mutate(
    std_weight_PatientExperience = 0.22,
    std_weight_Readmission = 0.22,
    std_weight_Mortality = 0.22,
    std_weight_safety = 0.22,
    std_weight_Process = 0.12,
    summary_score = NA_real_
  )

for (k in 1:nrow(all_df)) {
  grp_score <- unlist(summary_score[k, -1])[1:5]
  w         <- unlist(summary_score[k, -1])[6:10]
  i <- ifelse(is.na(grp_score), 1, 0)
  weight <- w / (1 - sum(w * i))
  sum_weight_ave <- (1-i) * weight * replace_na(grp_score, 0)
  summary_score[k, ]$summary_score <- sum(sum_weight_ave)
}
```


```{r}

report <- function(indsn, measure_OM, measure_OS,
                   measure_or, measure_ptexp, measure_process) {
  tibble(
      PROVIDER_ID = indsn$PROVIDER_ID,
      Outcomes_Mortality_cnt   = rowSums(!is.na(indsn[, measure_om])),
      Outcomes_safety_cnt      = rowSums(!is.na(indsn[, measure_OS])),
      Outcomes_Readmission_cnt = rowSums(!is.na(indsn[, measure_or])),
      Patient_Experience_cnt   = rowSums(!is.na(indsn[, measure_ptexp])),
      Process_cnt              = rowSums(!is.na(indsn[, measure_process])),
    ) %>%
    mutate(
      Total_measure_group_cnt = (Outcomes_Mortality_cnt >= 3) +
        (Outcomes_safety_cnt >= 3) + (Outcomes_Readmission_cnt >= 3) +
        (Patient_Experience_cnt >= 3) + (Process_cnt >= 3),
      MortSafe_Group_cnt = (Outcomes_Mortality_cnt >= 3) +
        (Outcomes_safety_cnt >= 3),
      report_indicator = as.integer(
        (MortSafe_Group_cnt >= 1) & (Total_measure_group_cnt >= 3)
      )
    )
}

report_indicator <- report(std_data_analysis_df, measure_om, measure_os,
                           measure_or, measure_ptexp, measure_process)

summary_score21 <-
  summary_score %>%
  inner_join(report_indicator, by = 'PROVIDER_ID') %>%
  arrange(PROVIDER_ID)

summary_score22 <-
  summary_score21 %>%
  filter(report_indicator == 1) %>%
  mutate(
    total_grp = (Outcomes_Mortality_cnt >= 3) + (Outcomes_safety_cnt >= 3) + 
      (Outcomes_Readmission_cnt >= 3) + (Patient_Experience_cnt >= 3) +
      (Process_cnt >= 3),
    cnt_grp = case_when(
      Total_measure_group_cnt == 3 ~ '1) # of groups=3       ',
      Total_measure_group_cnt == 4 ~ '2) # of groups=4       ',
      Total_measure_group_cnt == 5 ~ '3) # of groups=5       '
    )
  )
```


This is where the translation fails. The first call to `amap::Kmeans()` in the function `kmeans_macro()` gets the same results as SAS, but the second call doesn't. In SAS, the second call uses the argument `strict=1`, and I haven't found an R implementation of k-means with that option.

```{r}

kmeans_macro <- function(in_df) {
  s1 <- setNames(
    quantile(in_df$summary_score, probs = 0.2*(1:5), type=1),
    str_c("P", 20*(1:5))
  )
  s2 <-
    in_df %>%
    transmute(
      PROVIDER_ID,
      summary_score,
      P20 = s1['P20'],
      P40 = s1['P40'],
      P60 = s1['P60'],
      P80 = s1['P80'],
      grp = case_when(
        summary_score <= P20 ~ 1,
        summary_score <= P40 ~ 2,
        summary_score <= P60 ~ 3,
        summary_score <= P80 ~ 4,
        TRUE                 ~ 5,
      )
    )
  s3 <-
    s2 %>%
    group_by(grp) %>%
    summarize(
      NObs = n(),
      summary_score_Median = median(summary_score)
    )
  s33 <-
    s3 %>%
    mutate(summary_score = summary_score_Median)
  seeds2 <- sas_proc_fastclus(in_df$summary_score, iter.max = 1000,
                              centers = s33$summary_score)$centers
  km <- sas_proc_fastclus(in_df$summary_score, iter.max = 1000,
                          centers = seeds2, strict = 1)

  Cluster_mean <- km$centers
  cluster_sort <-
    tibble(mean_summary_score_star = Cluster_mean[order(Cluster_mean)]) %>%
    mutate(cluster = 1:n()) %>%
    arrange(mean_summary_score_star) %>%
    mutate(star = 1:n())
  
  in_df %>%
    mutate(cluster = abs(km$cluster)) %>%
    inner_join(cluster_sort, by = "cluster") %>%
    select(PROVIDER_ID, cnt_grp, star)
}


cnt_s10 <- summary_score22 %>% filter(total_grp == 3)
cnt_s20 <- summary_score22 %>% filter(total_grp == 4)
cnt_s30 <- summary_score22 %>% filter(total_grp == 5)

cnt_s1 <- kmeans_macro(cnt_s10)
cnt_s2 <- kmeans_macro(cnt_s20)
cnt_s3 <- kmeans_macro(cnt_s30)

cnt_s_str <-
  rbind(cnt_s1, cnt_s2, cnt_s3) %>%
  arrange(PROVIDER_ID)

RESULTS <-
  summary_score21 %>%
  left_join(cnt_s_str, by = "PROVIDER_ID")
```



```{r}

nation_avg0 <- function(indata, var) {
  indata %>%
    summarize({{ var }} := mean(summary_score))
}

nation_avg_peer <- function(indata, var, gr) {
  indata %>%
    group_by({{ gr }}) %>%
    summarize({{ var }} := mean(summary_score), .groups = "drop") %>%
    pivot_wider(values_from = {{ var }}, names_from = {{ gr }},
                names_prefix = "Summary_Score_Nat_peer")
}

nation_avg <- function(indata, var) {
  indata %>%
    filter(total_cnt >= 3) %>%
    summarize({{ var }} := mean(grp_score, na.rm = TRUE))
}

summary_avg <- nation_avg0(RESULTS, Summary_Score_Nat)
summary_avg_peer <- nation_avg_peer(RESULTS, Summary_Score_Nat,
                                    Total_measure_group_cnt)

outcome_mortality_avg <- nation_avg(outcome_mortality_df, Out_Mrt_Grp_Score_Nat)
outcome_safety_avg <- nation_avg(outcome_safety_df, Out_Sft_Grp_Score_Nat)
outcome_readmission_avg <- nation_avg(outcome_readmission_df,
                                      Out_Readm_grp_Score_Nat)
ptexp_avg <- nation_avg(ptexpt_df, Pt_Exp_Grp_Score_Nat)
process_avg <- nation_avg(process_df, Prc_of_Care_Grp_Score_Nat)

NATIONAL_MEAN <-
  cbind(
    summary_avg, summary_avg_peer,
		outcome_mortality_avg, outcome_safety_avg, outcome_readmission_avg,
		ptexp_avg, process_avg
  )
```















# Scratch work

```{r}
temp_info_df <-
  all_info_df %>% filter(zip_date == "2021-04-01") %>% select(info_df) %>% unnest(info_df)
official_df <- temp_info_df %>% select(PROVIDER_ID = `Facility ID`, `Hospital overall rating`)

official_df
actual_star_df

#official_df %>%
my_star_df %>%
  full_join(official_df, by = c("provider_id"="PROVIDER_ID")) %>%
  count(`Hospital overall rating`, stars)

weird_prov_ids <-
  my_star_df %>%
  full_join(official_df, by = c("provider_id"="PROVIDER_ID")) %>%
  filter(replace_na(`Hospital overall rating`, "Not Available") == "Not Available") %>%
  filter(!is.na(stars)) %>%
  pull(provider_id)

temp_info_df %>%
  filter(`Facility ID` %in% weird_prov_ids)

all_data_df %>% filter(PROVIDER_ID %in% weird_prov_ids)
RESULTS %>% filter(PROVIDER_ID %in% weird_prov_ids)

all_sas_df %>% filter(zip_date == "2020-10-01") %>% select(sas_input_df) %>% unnest(sas_input_df)
```




```{r}
my_star_df <-
  RESULTS %>%
  select(provider_id = PROVIDER_ID, stars = star)
actual_star_df <-
  all_info_df %>%
  filter(zip_date == "2021-04-01") %>%
  select(info_df) %>%
  unnest(info_df) %>%
  select(provider_id = `Facility ID`, stars = `Hospital overall rating`) %>%
  mutate(
    stars = ifelse(stars == "Not Available", NA_character_, stars),
    stars = as.integer(stars)
  )

my_star_df %>%
  transmute(provider_id, my_stars = stars) %>%
  full_join(
    actual_star_df %>%
      transmute(provider_id, actual_stars = stars),
    by = "provider_id"
  ) %>%
  mutate(
    my_stars = ifelse(is.na(my_stars), "NA", as.character(my_stars)),
    actual_stars = ifelse(is.na(actual_stars), "NA", as.character(actual_stars)),
    same = (my_stars == actual_stars)
  ) %>%
  count(same)
```


```{r}
summary_df <-
  RESULTS %>%
  select(PROVIDER_ID, summary_score, cnt_grp, star)

std_score_re <- "Std_(.*)_score"
std_weight_re <- "std_weight_(.*)"

get_std_columns <- function(df, col_re) {
  df <- RESULTS %>% select(PROVIDER_ID, matches(col_re))
  colnames(df)[2:ncol(df)] <-
    sapply(colnames(df)[2:ncol(df)], function(x) str_match(x, col_re)[1,2])
  df
}
score_df <- get_std_columns(RESULTS, std_score_re)
weight_df <- get_std_columns(RESULTS, std_weight_re)

new_colnames <- c("PROVIDER_ID", "PatientExperience", "Readmission",
                  "Mortality", "Safety", "Process")
colnames(weight_df) <- new_colnames
score_df <- score_df %>%
  select(PROVIDER_ID, PatientExp, Outcomes_Readmission,
         Outcomes_Mortality, Outcomes_Safety, Process)
colnames(score_df) <- new_colnames

summary_df
score_df
weight_df
```



```{r}
actual_df <- read.csv("star_2021apr_cms.csv", colClasses = "character") %>%
  mutate(actual_stars = as.integer(star))

RESULTS$PROVIDER_ID[!(RESULTS$PROVIDER_ID %in% actual_df$PROVIDER_ID)]
actual_df$PROVIDER_ID[!(actual_df$PROVIDER_ID %in% RESULTS$PROVIDER_ID)]

all_data_df %>% filter(PROVIDER_ID == "400127")

RESULTS %>% select(PROVIDER_ID, star, cnt_grp) %>%
  full_join(actual_df %>% select(PROVIDER_ID, actual_stars), by = "PROVIDER_ID") %>%
  mutate(same = (star == actual_stars)) %>%
  count(same, star, actual_stars)

bad_provider_ids <-
  RESULTS %>% select(PROVIDER_ID, star, cnt_grp) %>%
  full_join(actual_df %>% select(PROVIDER_ID, actual_stars), by = "PROVIDER_ID") %>%
  mutate(same = (star == actual_stars)) %>%
  filter(is.na(same) | !same) %>%
  pull(PROVIDER_ID)

RESULTS %>% filter(PROVIDER_ID %in% bad_provider_ids) %>% count(star)
actual_df %>% filter(PROVIDER_ID %in% bad_provider_ids) %>% count(star)

weird_provider_ids <-
  actual_df %>% filter(PROVIDER_ID %in% bad_provider_ids, star != "") %>% pull(PROVIDER_ID)

RESULTS %>%
  filter(PROVIDER_ID %in% weird_provider_ids)

all_data_df %>%
  filter(PROVIDER_ID %in% weird_provider_ids)
```


